\documentclass[12pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath,amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage[margin=2.5cm]{geometry}

\title{AI-Based Code Development:\\A Sample Research Document}
\author{ABCD Research Group\\University of Limerick}
\date{\today}

\begin{document}

\maketitle

\begin{abstract}
This document serves as a test file for the ABCD LaTeX editor deployment.
It demonstrates standard LaTeX features including sections, mathematics,
references, and formatting that the editor should handle correctly.
\end{abstract}

\section{Introduction}

The ABCD Research Project examines how generative AI is changing software
engineering practice, computing education, and industry workflows. This
sample document is used to verify that the GitHub-backed LaTeX editing
workflow functions correctly.

\subsection{Research Questions}

\begin{enumerate}
    \item How does AI-assisted coding affect developer cognition?
    \item What are the implications for software quality?
    \item How should computing curricula adapt?
\end{enumerate}

\section{Mathematical Content}

To verify that the WASM-based LaTeX compiler handles mathematics correctly,
we include some representative formulas.

The Gaussian distribution is defined as:
\begin{equation}
    f(x) = \frac{1}{\sigma\sqrt{2\pi}} \exp\left(-\frac{(x-\mu)^2}{2\sigma^2}\right)
\end{equation}

For a matrix transformation $A \in \mathbb{R}^{m \times n}$, the singular
value decomposition is:
\begin{equation}
    A = U \Sigma V^T
\end{equation}

where $U \in \mathbb{R}^{m \times m}$ and $V \in \mathbb{R}^{n \times n}$
are orthogonal matrices.

\section{Code Listings}

A simple Python function demonstrating AI-assisted generation:

\begin{verbatim}
def fibonacci(n: int) -> list[int]:
    """Generate first n Fibonacci numbers."""
    if n <= 0:
        return []
    seq = [0, 1]
    while len(seq) < n:
        seq.append(seq[-1] + seq[-2])
    return seq[:n]
\end{verbatim}

\section{Conclusion}

This document confirms that the ABCD LaTeX editor correctly compiles
standard LaTeX documents with mathematical notation, lists, and code
blocks. The GitHub-backed save mechanism ensures all team members can
access the latest version.

\end{document}
